---
title: "Random Stock Analysis"
format: html
editor: visual
---

## Broadcom Inc. (AVGO)

```{r}
library(quantmod)
library(tidyverse)
library(lubridate)
library(quantmod)
library(dplyr)
library(prophet)
library(ggplot2)

```

## Grab Data

```{r}
rm (list=ls())
ticker <-"IBM"
getSymbols(ticker,from="2024-01-01")
```

### Box Plot Of Closing Prices



```{r}


plot_monthly_boxplot <- function(ticker, start_date = "2024-01-01") {
  
  # Download data
  getSymbols(ticker, from = start_date, auto.assign = TRUE)
  
  # Prepare tidy data
  df <- get(ticker) %>%
    fortify.zoo() %>%
    as_tibble() %>%
    rename(Date = Index, Close = paste0(ticker, ".Close")) %>%
    mutate(
      Month = floor_date(Date, "month"),
      MonthLabel = format(Month, "%b %Y"),
      MonthLabel = factor(MonthLabel, levels = unique(MonthLabel))
    )
  
  # Compute monthly mean
  monthly_mean <- df %>%
    group_by(MonthLabel) %>%
    summarize(MeanClose = mean(Close, na.rm = TRUE))
  
  # Plot
  ggplot(df, aes(x = MonthLabel, y = Close)) +
    geom_boxplot(fill = "skyblue", color = "gray20", outlier.alpha = 0.4) +
    geom_point(
      data = monthly_mean,
      aes(x = MonthLabel, y = MeanClose),
      color = "orange", size = 3
    ) +
    labs(
      title = paste("Monthly Closing Price Distribution for", ticker),
      subtitle = paste("From", start_date, "to", format(max(df$Date), "%Y-%m-%d")),
      x = "Month",
      y = "Closing Price ($)"
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

# 🧩 Example usage
plot_monthly_boxplot("IBM", start_date = "2025-06-01")
```
```










## First Plot

```{r}
chartSeries(get(ticker),type="line", theme=chartTheme('white'),name = ticker)
```

```{r}
chartSeries(get(ticker),type="candlesticks", 
            theme=chartTheme('white'), 
            subset='last 4 months',name = ticker)
```
```{r}
chartSeries(get(ticker),type="matchsticks",
            theme=chartTheme('white'), subset='last 6 months',name = ticker)
```
```{r}
chartSeries(get(ticker),type="bars", 
            theme=chartTheme('white'), subset='last 2 months',name = ticker)
```

```{r}
chartSeries(get(ticker),
            type="line", 
            theme=chartTheme('white'),
            TA="addEMA(n=100)",name = ticker)
```

```{r}
chartSeries(get(ticker),
            type="line", 
            theme=chartTheme('white'),
            TA="addRSI()",name = ticker)
```


```{r}
chartSeries(get(ticker),
            type="line", 
            theme=chartTheme('white'),
            TA="addMACD()",name = ticker,subset="last 4 months")
```

```{r}
returns <- periodReturn(get(ticker),
             period='monthly',
             subset=NULL,
             type='arithmetic',
             leading=TRUE,name = ticker)
barplot(returns)
```

```{r}
returns <- periodReturn(get(ticker),
             period='monthly',
             subset=NULL,
             type='log',
             leading=TRUE)
barplot(returns)


### The Prophet Has Spoken

```{r}

ticker <- "F"
forecast_start <- as.Date("2025-10-01")
forecast_days  <- 30
display_start  <- as.Date("2025-06-01")

getSymbols(ticker, from = "2024-01-01", auto.assign = TRUE)

df <- get(ticker) %>%
  fortify.zoo() %>%
  as_tibble() %>%
  rename(ds = Index, y = paste0(ticker, ".Close"))

train_data <- df %>% filter(ds < forecast_start)

m <- prophet(train_data)

future <- make_future_dataframe(m, periods = forecast_days)
future <- future %>% filter(ds >= forecast_start)

forecast <- predict(m, future)
recent_history <- df %>% filter(ds >= display_start)

# 🧭 Plot with legend
ggplot() +
  geom_line(data = recent_history, aes(x = ds, y = y, color = "Historical"),linewidth=1) +
  geom_line(data = forecast, aes(x = ds, y = yhat, color = "Forecast"),linewidth=1) +
  geom_ribbon(
    data = forecast,
    aes(x = ds, ymin = yhat_lower, ymax = yhat_upper, fill = "Uncertainty"),
    alpha = 0.2
  ) +
  labs(
    title = paste("Prophet Forecast for", ticker),
    subtitle = paste("30-Day Forecast Beginning", forecast_start),
    x = "Date",
    y = "Closing Price ($)",
    color = "Series",
    fill = "Interval"
  ) +
  scale_color_manual(values = c("Historical" = "darkblue", "Forecast" = "darkred")) +
  scale_fill_manual(values = c("Uncertainty" = "orange")) +
  theme_minimal() +
  theme(
    legend.position = "top",
    legend.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```


